---
title: "Case Study"
subtitle: "Biostatistics (MA482/BE482)"
author: "Wenxing Li, Katana Colledge, Pascal Liberge, and John Garrett"
date: "Updated: `r Sys.Date()`"
output: reyes482::ma482_word_format
---

```{r setup, include=FALSE}
reyes482:::ma482_setup()
```

```{r}
library(haven)
AD <- read_sav('NEDICES.sav')

```

### Data modifications

* demographics
* current medical consitions
* smoking (ever vs never)
* drinker (ever/at least once per week vs. never)
* medication
* rate their health (combine into 3 catagories: good/very good, fair, poor/very poor)  I don't like that they did that
* neurological disrders
*exlcuded 206 with AD diagnosed or detected by NEDICES so 5072 participants remaining
```{r}
AD <- AD[- grep(0, AD$AD),] #Exculed the original 206 diagnosed with Alzheimer

```

```{r}
#make death only (evital==1)
AD <- AD[AD$evital==1,]
```


```{r}
# https://www.drugs.com/drug-class/nonsteroidal-anti-inflammatory-agents.html

# list of NSAIDs
NSAIDs <- c("Asprin", "aspirina", "Bayer", "adiro", "tromalyt",
            "Acemetacin",
            "acetaminophen","paracetamol", "gelocatil",
            "Aceclofenac", 
            "Diclofenac", "voltaren", "cambia", "cataflam", "arthrotec", "zipsor", "zorvolex", "dyloject",
            "Droxicam",
            "diflunisal", "dolobid",
            "etodolac", "lodine",
            "Flurbiprofen", "ansaid",
            "fenoprofen", "nalfon", "profeno","fenortho",
            "Ibuprofen", "advil", "motrin", "IBU", "Motrin", "duexis", "advil", "ibu", "profen","proprinal", "nuprin", "midol", "haltran", "genpril", "caldolor", "addaprin", "actiprofren",
            "Isonixin",
            "Indomethacin", "indocin", "tivorbex",
            "Ketoprofen", "orudis", "oruvail",
            "Ketorolac", "Toradol", "sprix",
            "Tenoxicam", 
            "Meloxicam","mobic", "vivlodex", "qmiiz", "anjeso",
            "metamizole", "nolotil",
            "mefenamic", "ponstel",
            "Naproxen", "aleve", "vimovo", "anaprox","midol", "flanax", "prevacid", "naprosyn", "relief", "aflaxen",
            "Nabumetone", "naprosyn","relafen",
            "Niflumic acid",
            "oxaprozin","daypro",
            "Piroxicam", "feldrne",
            "Pentoxifylline","trental", "hemovas",
            "Sulindac", "clinoril",
            "tolemtin", "tolectin"
            )
NSAIDs <- tolower(NSAIDs)

#make all drug columns lowercase in r
AD$drug_1 = tolower(AD$drug_1)
AD$drug_2 = tolower(AD$drug_2)
AD$drug_3 = tolower(AD$drug_3)
AD$drug_4 = tolower(AD$drug_4)
AD$drug_5 = tolower(AD$drug_5)
AD$drug_6 = tolower(AD$drug_6)

AD[grepl(paste(NSAIDs, collapse="|"), 
         paste(AD$drug_1, AD$drug_2, AD$drug_3, AD$drug_4, AD$drug_5, AD$drug_6)),]

```



## Goal
We aimed to reevaluate the existing uncertainty regarding the effects of NSAIDs use on risk of AD by examining whether AD mortality is decreased in NSAIDs users compared to non-users.

## Analysis

Therefore, although mean and median values were reported, differences were compared using a nonparametric (Mann–Whitney U and Kruskal Wallis tests). The chi-square or Fisher p tests were used to analyze categorical variables. Participants were divided in NSAIDs users and non-users (reference category). And 95% CI.

evital - censoring
fdefunction - death date

```{r}
fit.AD <- coxph(Surv(fdefuncion, evital)~ education+bii1 +Pfeffer_1 + Comor12 + ii1 , data = AD)
#Couldn't find the cerebrovascular disease predictor

tidy(fit.AD, conf.int = TRUE, conf.level = 0.95,exponentiate = TRUE)

```


```{r}
fit2.AD <- coxph(Surv(fdefuncion, evital)~ age + sex +education + a1 + bii1 + bii1dd + bi1 + bi1d + mmpun + Comor12 + ii1 + ii2 + stroke_1, data = AD)

#Note: The living area and marital status predictors are not present in the published data

tidy(fit2.AD, conf.int = TRUE, conf.level = 0.95,exponentiate = TRUE)
```
